A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-16 draft.tex
Proofreading abstract refs #27

\begin{abstract} 
Splitting a population into multiple instances is a technique that has
been used extensively in recent years in order to help improve the
performance of nature-inspired optimization algorithms. Work on those
populations can be done in parallel, and they can interact asynchronously,
a fact that can be leveraged to create scalable implementations based
on, among other methods, distributed, multi-threaded, parallel, and
cloud-native computing.  However, the design of these cloud-native,
distributed, multi-population algorithms is not a trivial task. Coming
from monolithic (single-instance) solutions, adaptations at several
levels, from the algorithmic to the functional, must be made to
leverage the scalability, elasticity, (limited) fault-tolerance,
reproducibility, and cost-effectiveness of cloud systems while, at the
same time, conserving the intended functionality. Instead of an
evolutive approach, in this paper we propose to create from scratch a
cloud-native optimization framework that is able to include multiple
algorithms and use few parameters to work. This solution goes beyond
current state of the art via a framework that is able to support
different algorithms at the same time, work asynchronously, and also
be easily deployable to any cloud platform. We evaluate the
performance and scalability of this solution, together with the effect
other design parameters had on it; in particular, the number and the
size of populations with respect to problem size. The architecture and
the implemented platform is an excellent alternative for running
locally or in the cloud, thus proving that cloud-native bioinspired
algorithms perform better in their ``natural'' environment than other
kinds of algorithms, % Did we compare it to other kind of algorithms?
                     % If we didn't, this should go - JJ 
                     % Compared against GA and PSO and others from BBOB - Mario
                     % on the algorithm, not speedup 
                     % I like the sentence, If we did not prove it, 
                     % at least we build a tool that will allow
                     % algorithms to run in their natural environment.
                     % The focus of the Journal after all is in computer systems - M

and setting a new baseline for scaling and
performance in the cloud.
\end{abstract}

>>>>

\begin{abstract} 
Splitting a population into multiple instances is a technique that has
been used extensively in recent years in order to help improve the
performance of nature-inspired optimization algorithms. Work on those
populations can be done in parallel, and they can interact asynchronously,
a fact that can be leveraged to create scalable implementations based
on, among other methods, distributed, multi-threaded, parallel, and
cloud-native computing.  However, the design of these cloud-native,
distributed, multi-population algorithms is not a trivial task. Using
as a foundation monolithic (single-instance) solutions, adaptations at several
levels, from the algorithmic to the functional, must be made to
leverage the scalability, elasticity, (limited) fault-tolerance,
reproducibility, and cost-effectiveness of cloud systems while, at the
same time, conserving the intended functionality. Instead of an
evolutive approach, in this paper we propose a
cloud-native optimization framework created from scratch, that is able to include multiple
(population-based) algorithms without increasing the number of
parameters that need tuning. This solution goes beyond
current state of the art, since is able to support
different algorithms at the same time, work asynchronously, and also
be easily deployable to any cloud platform. We evaluate the
performance and scalability of this solution, together with the effect
other design parameters had on it; in particular, the number and the
size of populations with respect to problem size. The architecture and
the implemented platform is an excellent alternative for running
locally or in the cloud, thus proving that cloud-native bioinspired
algorithms perform better in their ``natural'' environment than other
kinds of algorithms, and setting a new baseline for scaling and
performance of this kind of algorithms in the cloud.
\end{abstract}
